---
title: "homework11"
author: "Anna Semik"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Homework Problem 1
Analyze the 68k PBMCs dataset in the same way as presented in the Seurat's guide with PBMC3k. Apply QC, PCA, jackstraw, clustering, and t-SNE to create figure similar to Figure 3b on Zheng et al. 2017. Note that there are differences between Zheng's original analysis and Seurat's analysis. Pay attentions to hyper-parameters that you must choose for this new bigger dataset.

Provide R markdown file with your codes and outputs.

Present the t-SNE visualization with 10 clusters as defined by K-means clustering

Reproduce Figure 3 but note difference in results: https://www.nature.com/articles/ncomms14049/figures/3
```{r}
library(dplyr)
library(Seurat)
library(patchwork)

hwp1.data <- Read10X(data.dir = "./hg19_hw/")
hwp1 <- CreateSeuratObject(counts = hwp1.data, project = "hw111", min.cells = 3, min.features = 200)
hwp1

```

```{r}
VlnPlot(hwp1, features = c("nFeature_RNA", "nCount_RNA"), ncol = 2, same.y.lims=TRUE, pt.size = FALSE)
```

QC

```{r}
hwp1[["percent.mt"]] <- PercentageFeatureSet(hwp1, pattern = "^MT-")
VlnPlot(hwp1, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = FALSE)
```

```{r}
FeatureScatter(hwp1, feature1 = "nCount_RNA", feature2 = "percent.mt") +
  FeatureScatter(hwp1, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
```
```{r}
hwp1 <- subset(hwp1, subset = nFeature_RNA > 200 & nFeature_RNA < 2300 & percent.mt < 12)
```

```{r}
hwp1 <- NormalizeData(hwp1)
```

preparation to PCA

```{r}
hwp1 <- FindVariableFeatures(hwp1, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(hwp1), 10)

# plot variable features with and without labels
plot1 <- VariableFeaturePlot(hwp1)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1
plot2
```

```{r}
all.genes <- rownames(hwp1)
hwp1<- ScaleData(hwp1, features = all.genes)
```

PCA on scaled data
```{r}
hwp1 <- RunPCA(hwp1, features = VariableFeatures(object = hwp1))
print(hwp1[["pca"]], dims = 1:5, nfeatures = 5)

VizDimLoadings(hwp1, dims = 1:2, reduction = "pca")
```

```{r}
DimPlot(hwp1, reduction = "pca")
DimHeatmap(hwp1, dims = 1, cells = 500, balanced = TRUE)
DimHeatmap(hwp1, dims = 1:15, cells = 500, balanced = TRUE)
```

Jackstraw
```{r}
# NOTE: This process can take a long time for big datasets, comment out for expediency. More
# approximate techniques such as those implemented in ElbowPlot() can be used to reduce
# computation time
hwp1 <- JackStraw(hwp1, num.replicate = 100)
hwp1 <- ScoreJackStraw(hwp1, dims = 1:20)

JackStrawPlot(hwp1, dims = 1:15)

ElbowPlot(hwp1)
```

Clustering
```{r}
hwp1 <- FindNeighbors(hwp1, dims = 1:10)
hwp1 <- FindClusters(hwp1, resolution = 0.5)

head(Idents(hwp1), 5)
```

tSNE
```{r}
hwp1 <- RunTSNE(hwp1, dims = 1:10)

png('hw_problem1.png')
DimPlot(hwp1, reduction = "tsne")
dev.off()
```

# Homework Problem 2
Create a hierachical clustering by applying K-means clustering to cells defined by each of 10 cluster. Try to find a suitable number of clusters (k) for each sub-population.
```{r}
hwp1$cluster = as.integer(Idents(hwp1))
```

```{r}
for (i in 1:10){
  cluster = hwp1[, hwp1$cluster == i]
  neighbours = FindNeighbors(cluster,dims=1:10)
  sub_clusters = FindClusters(neighbours)
  cluster$sub_clusters = Idents(sub_clusters)
  
  png(paste0("problem2_", i, ".png"))
  print(DimPlot(cluster, group.by = 'sub_clusters', label=TRUE))
  dev.off()
}
```

